The SMT Competition 2015--2018

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt

> * Rules
>
> - basically incorrect results are "ignored" by omitting the benchmark if the status is not known - this comment still remains. The authors updated the text. I see their points and analysis, which I appreciated, through I think that this is an issue that should be dealt with more care. Correctness is very important for solvers when checking in particular real benchmarks (HW- and SW-verification, etc).

DONE (updated to better motivate the removal of benchmarks with
disagreements; of course we agree that correctness is important)

> * Significance of the results
>
>  - the paper and its analysis now contain many numbers and data, which is very appropriate for e competition report in my opinion. But, basically, no explanation is in place. What I expect to get out of a report, other than commenting the numbers, is their explanation, e.g.: what are the techniques implemented in solvers that overall performed better? Rr better, what techniques implemented in solvers led to an efficient solvers on a particular benchmark? why such techniques led to positive results on benchmarks with (a) given structure/characteristics?

WONTFIX (while interesting, this is way out of scope for this paper.
We, as organizers, are not the developers of most of the solvers (nor
the source of most benchmarks), so there is no practical way for us to
determine what exactly was the cause for improvement)

@@

>  - last paragraph of Section 7.1 that gives motivations for MathTSAT and Z3 to be industrial-strenght tool, and states Z3 training, are either not clear or somehow not convincing as motivations. The paragraph should be clarified, or can be omitted.

DONE (the paragraph was added in response to earlier reviewer feedback
and has been rephrased)

### 2019-08-21 2018/report/SMT-COMP.tex
Remove less interesting organizational details

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and oversees the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with
IJCAR (as part of FLoC) in~2018.  Consequently, its date varies.
Competition results were presented on July~19 in 2015, on July~2 in
2016, on July~23 in 2017, and on July~13 in~2018.

@@

Tables~\ref{table:benchmarks-main-track}--\ref{table:benchmarks-unsat-core-track}
show the number of benchmarks that were used in each competition track
and division since~2015.  A dash indicates that no eligible benchmarks
were available, and hence the corresponding SMT-LIB logic was not
actually a competition division in that track and year.  The size of
divisions varies widely, from just one benchmark in ABVFP to~72,705
benchmarks in QF\_SLIA.

>>>>

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair~\cite{smt-bylaws}.
The competition chair then assembles a team of organizers, and
oversees the work for the next edition of the competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with
IJCAR (as part of FLoC) in~2018.  Consequently, its date varies.
During 2015--2018, the workshop always took place in July.

@@

Tables~\ref{table:benchmarks-main-track}--\ref{table:benchmarks-unsat-core-track}
show the number of benchmarks that were used in each competition track
and division since~2015.  A dash indicates that no eligible benchmarks
were available, and hence the corresponding SMT-LIB logic was not
actually a competition division in that track and year.  The size of
divisions varies widely, from just one benchmark in ABVFP to~\num{72705}
benchmarks in QF\_SLIA.
